\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/paper.tex
Fix intro

Phantom hosts are cheap to create, allowing for discardable \textbf{one-time use}
proxy servers to be used by clients. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
\scheme supports both IPv4 and IPv6, though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented a prototype implementation (Section~\ref{sec:implementation})
and deployed it on a 10~Gbps testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}).

>>>>

Phantom hosts are cheap to create, allowing for discardable or even one-time-use
proxy servers. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
\scheme supports both IPv4 and IPv6, though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented a prototype implementation (Section~\ref{sec:implementation})
and deployed it on a 10~Gbps testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}).  We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.
